On Secure Delegation of SampBQP with a Classical Client

### 2020-02-02 bqp.tex
Revamp sec:BQP to use protocol env

\begin{thm}
	Let $n$ be large enough to achieve negligible completeness and soundness for the corresponding $\QMA$ certificate checks.
	Then \protoref{BQP} is a $\QPIP_1$ and constant round protocol for $\BQP$ with negligible completeness and soundness.
\end{thm}

\floatname{algorithm}{Protocol}
\begin{algorithm}
	\caption{Protocol for $\BQP$}
	\label{proto:BQP}
	\begin{algorithmic}[1]
		\State The verifier sends $x$ to the prover
		\State The prover sends $2n$ copies of $\ket{\psi_x}$ to the verifier
		\State The verifier uses $n$ copies to check for $x\in L$, and the other $n$ copies to check for $x\in\overline{L}$
	\end{algorithmic}
\end{algorithm}

Now we generalize the previous construction to achieve blindness.
We denote the prover's action as $\cF$. That is, $\cF(x)=\ket{\psi_x}^{\otimes 2n}$.

\begin{algorithm}
	\caption{Blind Protocol for $\BQP$}
	\label{proto:BlindBQP}
	\begin{algorithmic}[1]
		\State Let $\lambda$ be the security parameter.
		\State Let $L$ be the depth of the circuit corresponding to $\cF$
		\State Let $n$ be large enough to achieve negligible completeness and soundness for the corresponding $\QMA$ certificate checks.
		\State The verifier runs $\mathsf{QHE.Keygen}(\lambda, L)$ to get $pk, sk$.
		\State The verifier encrypts $x$ to get $\mathsf{QHE.Enc}_{pk}(x)$
		\State The verifier sends $c=\mathsf{QHE.Enc}_{pk}(x)$ and $pk$ to the prover
		\State The prover sends $\mathsf{QHE.Eval}(\cF, c)$ to the verifier
		\State The verifier measures the incoming ciphertext according to \autoref{decodeMeasureOrder} and how it would've checked the $\QMA$ certificates
		\State The verifier decodes the measurement results
		\State The verifier uses $n$ copies to check for $x\in L$, and the other $n$ copies to check for $x\in\overline{L}$
	\end{algorithmic}
\end{algorithm}

>>>>

\begin{thm}
	\protoref{BQP} is a $\QPIP_1$ and constant round protocol for $\BQP$ with negligible completeness and soundness.
\end{thm}

\begin{protocol}{Protocol for $\BQP$}
	\label{proto:BQP}
	Let $n$ be the number of repetitions required to achieve negligible completeness and soundness for the corresponding $\QMA$ certificate checks.
	\begin{enumerate}
		\item The verifier sends $x$ to the prover
		\item The prover sends $2n$ copies of $\ket{\psi_x}$ to the verifier
		\item The verifier uses $n$ copies to check for $x\in L$, and the other $n$ copies to check for $x\in\overline{L}$
	\end{enumerate}
\end{protocol}

Now we compile \cref{proto:BQP} using $\mathsf{QHE}$ in order to achieve blindness.
We denote the honest prover's action in $\cref{proto:BQP}$ as $\cF$; that is, $\cF(x)=\ket{\psi_x}^{\otimes 2n}$.

\begin{protocol}{Blind Protocol for $\BQP$}
	\label{proto:BlindBQP}
	Let $\lambda$ be the security parameter.
	Let $L$ be the depth of the circuit corresponding to $\cF$.
	Let $n$ be number of repetitions required to achieve negligible completeness and soundness for the corresponding $\QMA$ certificate checks.
	\begin{enumerate}
		\item The verifier runs $\mathsf{QHE.Keygen}(\lambda, L)$ to get $pk, sk$.
		\item The verifier encrypts $x$ to get $\mathsf{QHE.Enc}_{pk}(x)$
		\item The verifier sends $c=\mathsf{QHE.Enc}_{pk}(x)$ and $pk$ to the prover
		\item The prover sends $\mathsf{QHE.Eval}(\cF, c)$ to the verifier
		\item The verifier measures the incoming ciphertext according to \autoref{decodeMeasureOrder} and how it would've checked the $\QMA$ certificates \Ethan{Not sure if rigorous enough}
		\item The verifier decodes the measurement results
		\item The verifier uses $n$ copies to check for $x\in L$, and the other $n$ copies to check for $x\in\overline{L}$
	\end{enumerate}
\end{protocol}
